---
title: "Results signalling in token offerings"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---

Packages
```{r}
#install packages
#probably not all packages were used
install.packages("dplyr")    #installation of the %>%
install.packages("knitr")
install.packages("lattice")
install.packages("tidyverse")
install.packages("likert")
install.packages("MASS")
install.packages("psych")
install.packages("viridis")
install.packages("ggplot2")
install.packages("here")
install.packages("flextable")
install.packages("devtools")
devtools::install_github("matherion/userfriendlyscience", dependencies=T)
# install klippy for copy-to-clipboard button in code chunks
remotes::install_github("rlesur/klippy")
install.packages("corrplot")
install.packages('REdaS')
install.packages("cowplot")
install.packages("car")
install.packages("vcd")
#installed.packages("psy")


# set options
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
# install packages
library(dplyr)    # alternatively, this also loads %>%
library(knitr)
library(lattice)
library(tidyverse)
library(likert)
library(MASS)
library(psych)
library(viridis)
library(ggplot2)
library(here)
library(flextable)
library(devtools)
library(userfriendlyscience)
# activate klippy for copy-to-clipboard button
klippy::klippy()
library(corrplot)
library(REdaS)
library(cowplot)
library (car)
library(psych)
library(vcd)
```
experience contingency table
When the code does not work, load the libraries. There is a filter function in a default library. This library is used after session restarting (the last loaded is used, if no is loaded then default). The problem can be solved with specifying the intended library.
```{r}
ds <- filter(ds, ds$E004 == 'Yes, I have correctly answered all questions. My data can be used for scientific purposes.') #Filter scientific purposes
#filter entries with -1 at every signal?
table(ds$I001, ds$I006, exclude = NULL) #report NAs
ds <- ds %>% filter_at(vars(I001,I006),all_vars(!is.na(.))) #Filter no answers  at investors
table(ds$I001, ds$I006)
```
Make one data set according to the investor group
```{r}
ds_inv <- dplyr::filter(ds, ds$I001 == 'Yes') #token offering investors
ds_no_inv <- filter(ds, ds$I001 == 'No') #no token offering investors
ds_pre <- filter(ds_inv, ds_inv$I004 == 'Yes') #pre-ICO investors
ds_no_pre <- filter(ds_inv, ds_inv$I004 == 'No') #no pre-ICO investors
ds_crypto <- filter(ds, (ds$I001 == 'Yes' | ds$I006 == 'Yes'))#crypto experienced investors
ds_no_crypto <- filter(ds, (ds$I001 == 'No' | ds$I006 == 'No'))#No crypto experienced investors
```

Data sets for the signals
```{r}
#signals with all investors
ds_t_sig <- data.frame(ds$I001, ds$TS01_01, ds$TS01_04, ds$TS01_05, ds$TS01_06, ds$TS01_07) #technological signals ds[,20:24] would do the same, would be probably better
ds_f_sig <- data.frame(ds$I001,ds$FS01_01,ds$FS01_02, ds$FS01_04, ds$FS01_05, ds$FS01_06, ds$FS01_07, ds$FS01_08, ds$FS01_09, ds$FS01_10, ds$FS01_28, ds$FS01_29, ds$FS01_16, ds$FS01_17, ds$FS01_18, ds$FS01_19, ds$FS01_20, ds$FS01_21, ds$FS01_22, ds$FS01_23, ds$FS01_24, ds$FS01_25, ds$FS01_26, ds$FS01_27, ds$FS02_11, ds$FS02_12, ds$FS02_13, ds$FS02_14, ds$FS02_15, ds$FS03_11, ds$FS03_12, ds$FS03_13, ds$FS03_14) #financial signals
ds_i_sig <- data.frame(ds$I001,ds$IS01_01, ds$IS01_02, ds$IS02_01, ds$IS02_02, ds$IS02_03, ds$IS02_04, ds$IS03_01) #ideological signals
ds_sig <- ds[,20:63] #all signals (only signals)
ds_sig_inv <- ds_inv[,20:63]
```

No offering reasons
```{r}
option_no <- c("Never heard about it", "Too risky", "Did not find the right project", "Not interested in investing into token offerings", "No experience in financial investing (like ETFs, shares or bonds)", "No experience in alternative investing (like cryptocurrencies or crowdfunding)", "Other")
#count true values
answer_no <- c(sum(ds$I002_01, na.rm = TRUE), sum(ds$I002_02, na.rm = TRUE), sum(ds$I002_03, na.rm = TRUE), sum(ds$I002_04, na.rm = TRUE), sum(ds$I002_06, na.rm = TRUE), sum(ds$I002_07, na.rm = TRUE), sum(ds$I002_05, na.rm = TRUE)) 
ds_no_answ <- data.frame(option_no, answer_no)
require(tidyr)
ds_no_answ.long <- gather(ds_no_answ, variable,value, -option_no)
#maybe add the percentage within the bar or work just with percentages?, maybe change the color?
no_inv_barplot <- ggplot(data = ds_no_answ.long, aes(x = reorder(option_no, answer_no), y = value)) + #, fill = variable for color
  geom_col(position = position_dodge()) +
  coord_flip() +
  theme(axis.title.x=element_blank(), #remove axis title
        axis.title.y=element_blank())

cowplot::save_plot(here("plot", "no_inv_barplot.png"), # where to save the plot
                   no_inv_barplot,        # object to plot
                   base_asp = 1.5,  # ratio of space fro questions vs space for plot
                   base_height = 8) # size! higher for smaller font size

#prepare data for correlation plot
ds_no_for_cor <- data.frame(ds$I002_01, ds$I002_02, ds$I002_03, ds$I002_04, ds$I002_06, ds$I002_07, ds$I002_05)
#ds_no_for_cor <- setNames(ds_no_for_cor, option_no) #change names here
name_list <- list(c("A: Never heard about it", "B: Too risky", "C: Did not find the right project", "D: Not interested in investing into token offerings", "E: No experience in financial investing (like ETFs, shares or bonds)", "F: No experience in alternative investing (like cryptocurrencies or crowdfunding)", "G: Other"), c("A", "B", "C", "D", "E", "F", "G"))
ds_no_for_cor <- ds_no_for_cor  %>% filter(!is.na(.)) #filters every NA
no_cor <- cor(ds_no_for_cor)
no_cor <- structure(no_cor, .Dimnames = name_list)
#corrplot(no_cor, tl.srt = 45, tl.cex = 0.6) #corrMatrix, degree of text, text size

# correlation plot: draw ellipses + decorations
corrplot(no_cor, type="upper", method="ellipse",
         tl.pos="lt", tl.col="black",  tl.offset=1, tl.srt=0, tl.cex = 0.7) #tl.cex = 0.6 -> text size
# draw labels in black (disabling all the other stuff already drawn)
corrplot(no_cor, add=T, type="lower", method="number",
         col="black", diag=F, tl.pos="n", cl.pos="n")
# if you don't like the lines on the diagonal, (ie diag="n" of corrplot.mixed),
#  having a look at corrplot.mixed yields the following code:
n <- nrow(no_cor)
symbols(1:n, n:1, add=TRUE, bg="white", fg="grey", inches=F, squares=rep(1, n))

#cowplot::save_plot(here("plot", "no_inv_corrplot.png"), # where to save the plot
 #                  no_inv_corrplot,        # object to plot
  #                 base_asp = 1.5,  # ratio of space fro questions vs space for plot
   #                base_height = 8) # size! higher for smaller font size

#plot all answers for other without NAs
ds$I002_05a[!is.na(ds$I002_05a)]

```
token offering investor
```{r}
#motivation
motives <- data.frame(ds_inv$I003)
motives$ds_inv.I003 <- as.character(as.character(motives$ds_inv.I003)) #looks useless but works (otherwise it would display following warning: invalid factor level, NA generated)
motives[motives == "Technological motives (you are personally enthusiastic about the venture's technology and business model/idea)"] <- 'Technological'
motives[motives == "Financial motives (you are interested in financial gains and an equity stake in the venture)"] <- 'Financial'
motives[motives == "Ideological motives (you want to use the token for the intended function, disrupt established structures, sell the token for a higher price or you have social motives)"] <- 'Ideological'


ggplot(motives,
       aes(x=reorder(ds_inv.I003,ds_inv.I003,
                     function(x) length(x)))) +
       geom_bar() +
  coord_flip() +
  theme(axis.title.x=element_blank(), #remove axis title
        axis.title.y=element_blank(),
        axis.text=element_text(size=15))


table(ds$I004, ds$I005)
```
Correlation motive and pre-ICO / investor type
```{r}
#https://stats.stackexchange.com/questions/108007/correlations-with-unordered-categorical-variables 
ds_inv_cor <- ds_inv[,17:19]
ds_inv_cor <- ds_inv_cor  %>% filter(!is.na(.)) #filters every NA

assocstats(table(ds_inv_cor$I003, ds_inv_cor$I004))

#myabe the rest is useless
ds_inv_cor$I003 <- as.character(as.character(ds_inv_cor$I003))
ds_inv_cor$I004 <- as.character(as.character(ds_inv_cor$I004))
ds_inv_cor$I005 <- as.character(as.character(ds_inv_cor$I005))

ds_inv_cor[ds_inv_cor == "Technological motives (you are personally enthusiastic about the venture's technology and business model/idea)"] <- 1
ds_inv_cor[ds_inv_cor == "Financial motives (you are interested in financial gains and an equity stake in the venture)"] <- 2
ds_inv_cor[ds_inv_cor == "Ideological motives (you want to use the token for the intended function, disrupt established structures, sell the token for a higher price or you have social motives)"] <- 3

ds_inv_cor[ds_inv_cor == "Yes"] <- 1
ds_inv_cor[ds_inv_cor == "No"] <- 2

ds_inv_cor[ds_inv_cor == "Private"] <- 1
ds_inv_cor[ds_inv_cor == "Professional"] <- 2

ds_inv_cor$I003 <- as.numeric(as.character(ds_inv_cor$I003))
ds_inv_cor$I004 <- as.numeric(as.character(ds_inv_cor$I004))
ds_inv_cor$I005 <- as.numeric(as.character(ds_inv_cor$I005))

cor_inv <- cor(ds_inv_cor)
```

Found
```{r}
#bar plot all options
option_f <- c("Discord", "Reddit", "Twitter", "Facebook", "LinkedIn", "Telegram", "Bitcointalk", "Instagram", "Niklas personally", "WhatsApp", "Other")

#count true values
answer_f_no <- c(sum(ds_no_inv$E006_01, na.rm = TRUE), sum(ds_no_inv$E006_02, na.rm = TRUE), sum(ds_no_inv$E006_03, na.rm = TRUE), sum(ds_no_inv$E006_04, na.rm = TRUE), sum(ds_no_inv$E006_05, na.rm = TRUE), sum(ds_no_inv$E006_06, na.rm = TRUE), sum(ds_no_inv$E006_07, na.rm = TRUE), sum(ds_no_inv$E006_08, na.rm = TRUE), sum(ds_no_inv$E006_09, na.rm = TRUE), sum(ds_no_inv$E006_10, na.rm = TRUE), sum(ds_no_inv$E006_11, na.rm = TRUE)) 

answer_f <- c(sum(ds_inv$E006_01, na.rm = TRUE), sum(ds_inv$E006_02, na.rm = TRUE), sum(ds_inv$E006_03, na.rm = TRUE), sum(ds_inv$E006_04, na.rm = TRUE), sum(ds_inv$E006_05, na.rm = TRUE), sum(ds_inv$E006_06, na.rm = TRUE), sum(ds_inv$E006_07, na.rm = TRUE), sum(ds_inv$E006_08, na.rm = TRUE), sum(ds_inv$E006_09, na.rm = TRUE), sum(ds_inv$E006_10, na.rm = TRUE), sum(ds_inv$E006_11, na.rm = TRUE)) 

ds_f <- data.frame(option_f, answer_f, answer_f_no)
require(tidyr)
ds_f.long <- gather(ds_f, Group,value, -option_f)
#maybe add the percentage within the bar or work just with percentages?, maybe change the color?
ggplot(data = ds_f.long, aes(x = option_f, y = value, fill = Group)) + #x = reorder(option_no, answer_no), y = value
  geom_col(position = position_dodge()) +
  coord_flip() +
  theme(axis.title.x=element_blank(), #remove axis title
        axis.title.y=element_blank()) +
  scale_fill_discrete(labels=c('Token offering investor','No token offering investor')) #change label in the legend, maybe change colors with scale_... too?

#try to change the color
ggplot(data = ds_f.long, aes(x = option_f, y = value, fill = Group)) + #x = reorder(option_no, answer_no), y = value
  geom_col(position = position_dodge()) +
  coord_flip() +
  theme(axis.title.x=element_blank(), #remove axis title
        axis.title.y=element_blank()) +
  #scale_fill_discrete(labels=c('Token offering investor','No token offering investor'), values=c("#9933FF", "#33FFFF")) +
                      scale_fill_manual(labels=c('Token offering investor','No token offering investor'), values=c("#99C000",
                             "#0083CC"))

#plot all answers for other without NAs
ds$E006_11a[!is.na(ds$E006_11a)]
```



Test H1: Pre-sale investors care less about signals.
Avg(pre-ICO) < Avg(not-pre-ico)
```{r}
#to make a dataframe with only the signals: ds_inv[,20:63] but control indices before!
lik_pre <- lik_ds(ds_pre[,20:63])
avg_pre <- mean(lik_pre[,1])
avg_pre_idk <- mean(lik_pre[,2])

lik_no_pre <- lik_ds(ds_no_pre[,20:63])
avg_no_pre <- mean(lik_no_pre[,1])
avg_no_pre_idk <- mean(lik_no_pre[,2])

if(avg_pre < avg_no_pre){
  print(paste("Because Avg(pre-ICO)", avg_pre, "< Avg(not-pre-ico)", avg_no_pre, "H1 is true --> Pre-sale investors care less about signals."))
}else{
  print(paste("Because Avg(pre-ICO)", avg_pre, "> Avg(not-pre-ico)", avg_no_pre, "H1 is false --> Pre-sale investors do not care less about signals."))
  print(paste("Pre-ICo investors seems to be better educated about token offerings, because they have more often an answer to the questions", "avg_pre_idk:", avg_pre_idk, "avg_no_pre_idk", avg_no_pre_idk))
}

ds_H1 <- cbind( data.frame(ds_inv$I004), ds_inv[,20:63]) #prepare data for the tests
ds_H1[ds_H1 == -1] <- NA
ds_H1 <- filter(ds_H1, is.null(ds_H1$I004))

#Levene test to test for varicance homogenity (for the t-test)
lvt <- leveneTest(ds_H1[,2] ~ ds_inv.I004, data = ds_H1)
print(lvt)
#p value 0.4 -> alternative hypothesis -> different variances
leveneTestOnDS(ds_H1)
#because 41 of 44 columns have heterogene variances perform the Welch vesion of the t-test

#t-test
#replace every -1 with a NA to not bias the average with the -1 entries
#this results in a smaller effect on the average when a signal has more idk answers, this effect is no problem because a signal with bad oberservability is a bad signal
#the effect can be compared with the averages above where every signal has the same effect regardless of the idk answers
pre_NA <- ds_pre[,20:63]
pre_NA[pre_NA == -1] <- NA #replaces every -1 with a NA
no_pre_NA <- ds_no_pre[,20:63]
no_pre_NA[no_pre_NA == -1] <- NA #replaces every -1 with a NA
t.test(pre_NA, no_pre_NA, "greater")
```
Test H2: People who never invested in the crypto context rely more on signals based on external certification.
Avg(external certification | no-crypto-exp) > Avg(external certification | crypto-exp)
```{r}
ds_crypto_ex <- cbind(data.frame(ds_crypto$TS01_04, ds_crypto$TS01_05), ds_crypto[28:35], data.frame(ds_crypto$FS01_26)) #not sure if stages are an external signal #cbind() – combining the columns of two data frames side-by-side
ds_no_crypto_ex <- cbind(data.frame(ds_no_crypto$TS01_04, ds_no_crypto$TS01_05), ds_no_crypto[28:35], data.frame(ds_no_crypto$FS01_26)) #not sure if stages are an external signal #cbind() – combining the columns of two data frames side-by-side
lik_crypto_ex <- lik_ds(ds_crypto_ex)
avg_crypto_ex <- mean(lik_crypto_ex[,1])

lik_no_crypto_ex <- lik_ds(ds_no_crypto_ex)
avg_no_crypto_ex <- mean(lik_no_crypto_ex[,1])

#prepare data for the tests
exp <- rep('Yes', times = nrow(ds_crypto_ex))
ds_H2_ex <- cbind(exp, ds_crypto_ex)

no_exp <- rep('No', times = nrow(ds_no_crypto_ex))
ds_H2_no_ex <- cbind(no_exp, ds_no_crypto_ex)

#rename column names before using rbind
colnames(ds_H2_ex) <- 1:ncol(ds_H2_ex) #gives the columns names from 1 to n
colnames(ds_H2_no_ex) <- 1:ncol(ds_H2_ex) #gives the columns names from 1 to n
ds_H2 <- rbind(ds_H2_ex, ds_H2_no_ex)

ds_H2[ds_H2 == -1] <- NA #replaces every -1 with a NA
ds_no_crypto_ex[ds_no_crypto_ex == -1] <- NA
ds_crypto_ex[ds_crypto_ex == -1] <- NA

leveneTestOnDS(ds_H2)
#all columns different variances, if -1 is not replaced then only one column

t.test(ds_no_crypto_ex, ds_crypto_ex,  alternative = "greater")
t.test(ds_crypto_ex, ds_no_crypto_ex,  alternative = "greater")
```

Test H3: There is a different valuation of signals, depending on the investors group.
Avg(financial signals | financial motivated) >  Avg(financial signals | not financial motivated) and so on
Additionally: factor analysis
```{r}
ds_t_inv <- filter(ds, ds$I003 == "Technological motives (you are personally enthusiastic about the venture's technology and business model/idea)") #technological motivated investors
ds_f_inv <- filter(ds_inv, ds_inv$I003 == "Financial motives (you are interested in financial gains and an equity stake in the venture)")#financial motivated investors
ds_i_inv <- filter(ds_inv, ds_inv$I003 == "Ideological motives (you want to use the token for the intended function, disrupt established structures, sell the token for a higher price or you have social motives)")#ideological motivated investors
ds_no_t_inv <- filter(ds, ds$I003 != "Technological motives (you are personally enthusiastic about the venture's technology and business model/idea)") #no technological motivated investors
ds_no_f_inv <- filter(ds_inv, ds_inv$I003 != "Financial motives (you are interested in financial gains and an equity stake in the venture)")#no financial motivated investors
ds_no_i_inv <- filter(ds_inv, ds_inv$I003 != "Ideological motives (you want to use the token for the intended function, disrupt established structures, sell the token for a higher price or you have social motives)")#no ideological motivated investors

lik_t_inv <- lik_ds(ds_t_inv[,20:24])
lik_f_inv <- lik_ds(ds_f_inv[25:56])
lik_i_inv <- lik_ds(ds_i_inv[57:63])
lik_no_t_inv <- lik_ds(ds_no_t_inv[,20:24])
lik_no_f_inv <- lik_ds(ds_no_f_inv[25:56])
lik_no_i_inv <- lik_ds(ds_no_i_inv[57:63])

avg_t_inv <- mean(lik_t_inv[,1])
avg_f_inv <- mean(lik_f_inv[,1])
avg_i_inv <- mean(lik_i_inv[,1])
avg_no_t_inv <- mean(lik_no_t_inv[,1])
avg_no_f_inv <- mean(lik_no_f_inv[,1])
avg_no_i_inv <- mean(lik_no_i_inv[,1])

#test again without "A whitepaper is published" as the existence of a whitepaper should not be a signal
#and maybe sum the country in one variable as it controls for one signal, so it is not over proportional in the average
#same for factor analysis?
#do the factor analysis one time with the whole data set and one time with token offering investors?
lik_t_inv_w <- lik_ds(cbind(ds_t_inv[,20:22], data.frame(ds_t_inv$TS01_07)))
avg_t_inv_w <- mean(lik_t_inv_w[,1])
lik_no_t_inv_w <- lik_ds(cbind(ds_no_t_inv[,20:22], data.frame(ds_no_t_inv$TS01_07)))
avg_no_t_inv_w <- mean(lik_no_t_inv_w[,1])
#result stays the same

#technological
#Levene
ds_H3_t <- combine_ds_before_levene(ds_t_inv[,20:24], ds_no_t_inv[,20:24])
leveneTestOnDS(ds_H3_t$result) #5 -> heterogeneous variance

#t-tests
t.test(ds_H3_t$ds1, ds_H3_t$ds2, alternative = "greater")
t.test(ds_H3_t$ds2, ds_H3_t$ds1, alternative = "greater")

#financial
ds_H3_f <- combine_ds_before_levene(ds_f_inv[25:56], ds_no_f_inv[25:56])
leveneTestOnDS(ds_H3_f$result) #28 -> 
t.test(ds_H3_f$ds1, ds_H3_f$ds2, alternative = "greater")

#ideological
ds_H3_i <- combine_ds_before_levene(ds_i_inv[25:56], ds_no_i_inv[25:56])
leveneTestOnDS(ds_H3_i$result) #27 -> heterogeneous variance
t.test(ds_H3_i$ds1, ds_H3_i$ds2, alternative = "greater")

KMOS(ds_sig)
cortest.bartlett(ds_sig) #p.value 0 --> Items correlate significantly

nfactors(ds_sig, rotate="varimax", fm="mle") #typically look at map test

fafitfree <- fa(ds_sig, nfactors = ncol(ds_sig[,-c(44)]), rotate = "none")
n_factors <- length(fafitfree$e.values)

scree <- data.frame(
     Factor_n =  as.factor(1:n_factors), 
     Eigenvalue = fafitfree$e.values)
ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
     geom_point() + geom_line() +
     xlab("Number of factors") +
     ylab("Initial eigenvalue") +
     labs( title = "Scree Plot", 
           subtitle = "(Based on the unreduced correlation matrix)")


#parallel analysis
#ev <- eigen(cor(ds_sig))
#op <- parallelplot(subject=nrow(ds_sig), var = ncol(ds_sig), rep = 100, cent = .05)
#nS <- nScreen(x= ev$values, aparallel)

factanal(ds_sig, 9, rotatoin="varimax")


#for investors
KMOS(ds_sig_inv)
cortest.bartlett(ds_sig_inv) #p.value 3.445e-225 --> Items correlate significantly

fafitfree <- fa(ds_sig_inv, nfactors = ncol(ds_sig_inv[,-c(44)]), rotate = "none")
n_factors <- length(fafitfree$e.values)
scree     <- data.frame(
  Factor_n =  as.factor(1:n_factors), 
  Eigenvalue = fafitfree$e.values)
ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
  geom_point() + geom_line() +
  xlab("Number of factors") +
  ylab("Initial eigenvalue") +
  labs( title = "Scree Plot", 
        subtitle = "(Based on the unreduced correlation matrix)")

nfactors(ds_sig_inv, rotate="varimax", fm="mle") #typically look at map test
fa <- factanal(ds_sig_inv, 4, rotatoin="varimax")
fa



```
H4: Technological signals are rated higher than non-technological signals.
```{r}
lik_inv_tech <- lik_ds(ds_inv[,20:24])
lik_inv_no_tech <- lik_ds(ds_inv[,25:63])
avg_inv_tech <- mean(lik_inv_tech[,1])
avg_inv_no_tech <- mean(lik_inv_no_tech[,1])

lik_no_inv_tech <- lik_ds(ds_no_inv[,20:24])
lik_no_inv_no_tech <- lik_ds(ds_no_inv[,25:63])
avg_no_inv_tech <- mean(lik_no_inv_tech[,1])
avg_no_inv_no_tech <- mean(lik_no_inv_no_tech[,1])
#--> H4 true

#because different variables no Levene test possible (and somewhat useless)
H4_1 <- ds_inv[,20:24]
H4_1[H4_1 == -1] <- NA #replaces every -1 with a NA

H4_2 <- ds_inv[,25:63]
H4_2[H4_2 == -1] <- NA #replaces every -1 with a NA
t.test(H4_1, H4_2, alternative = "greater")

#Test again without Whitepaper
H4_1_w <- cbind(ds_t_inv[,20:22], data.frame(ds_t_inv$TS01_07))
lik_inv_tech_w <- lik_ds(H4_1_w)
H4_1_w[H4_1_w == -1] <- NA #replaces every -1 with a NA
t.test(H4_1_w, H4_2, alternative = "greater")
```
H5: Technological and ideological motivated investors value open-source code as positive while financial motivated investors assess code on GitHub as negative.
```{r}
print(lik_avg_idk(ds_t_inv[,20]))
print(lik_avg_idk(ds_i_inv[,20]))
print(lik_avg_idk(ds_f_inv[,20]))
#--> H5 false

#maybe financial motivated investors believe that the code is fine and it is no scam when the code is public and for investors with programming expertise is public code per se not a signal just the code quality??? --> avenue for further research?
```


Signals Likert
```{r}
lbs <- c("Strongly against investment", "Against investment", "Neutral",  "Pro investment", "Strongly pro investment") #labels
#see https://jakec007.github.io/assets/files/2021-06-23-R-likert.pdf page 6 and the following

#mean and idk
lik_inv <- lik_ds(ds_inv[,20:63])
lik_no_inv <- lik_ds(ds_no_inv[,20:63])

lik_inv <- round(lik_inv, 2)
lik_no_inv <- round(lik_no_inv, 2)

t_inv <- compare_with_3(ds_inv[,20:63])
t_no_inv <- compare_with_3(ds_no_inv[,20:63])

#Technological signals
#No investor first
T1n <- paste('Ta: The code is hosted publicly on GitHub', 'Mean (No / Yes):', lik_no_inv[1,1], t_no_inv[1,5], '/',  lik_inv[1,1], t_inv[1,5], "I don't know / not specified (Idk) (No / Yes):", lik_no_inv[1,2], '/', lik_inv[1,2])
T2n <- paste("Tb: Professional security audit when the source code is public", 'Mean:', lik_no_inv[2,1], t_no_inv[2,5], '/',  lik_inv[2,1], t_inv[2,5], "Idk:", lik_no_inv[2,2], '/', lik_inv[2,2])
T3n <- paste("Tc: Professional security audit when the source code is private", 'Mean:', lik_no_inv[3,1], t_no_inv[3,5], '/',  lik_inv[3,1], t_inv[3,5], "Idk:", lik_no_inv[3,2], '/', lik_inv[3,2])
T4n <- paste("Td: A whitepaper is published", 'Mean:', lik_no_inv[4,1], t_no_inv[4,5], '/',  lik_inv[4,1], t_inv[4,5], "Idk:", lik_no_inv[4,2], '/', lik_inv[4,2])
T5n <- paste("Te: The whitepaper provides technically detailed but precise and understandable information", 'Mean:', lik_no_inv[5,1], t_no_inv[5,5], '/',  lik_inv[5,1], t_inv[5,5], "Idk:", lik_no_inv[5,2], '/', lik_inv[5,2] )

colnames(ds_t_sig) <- c('Investor group', T1n, T2n, T3n, T4n, T5n) #colnames need every colum name to be renamed but accepts variables (rename does not accept variables)

likert_t_sig <- ds_t_sig %>%
  dplyr::mutate_if(is.character, factor) %>%
  dplyr::mutate_if(is.numeric, factor, levels = 1:5, labels = lbs) %>%
  #drop_na() %>% #drops IDK?
  as.data.frame()

likert_plot_t_sig <- plot(likert(likert_t_sig[,2:6], grouping = likert_t_sig[,1])) #grouped by investor group

cowplot::save_plot(here("plot", "likert_plot_t_sig.png"), # where to save the plot
                   likert_plot_t_sig,        # object to plot
                   base_asp = 1.5,  # ratio of space fro questions vs space for plot
                   base_height = 6) # size! higher for smaller font size

#those naming rows should be refactored!!!
#Financial signals
F1n <- paste('Fa: No soft cap', 'Mean (No / Yes):', lik_no_inv[6,1], t_no_inv[6,5], '/',  lik_inv[6,1], t_inv[6,5], "I don't know / not specified (Idk) (No / Yes):", lik_no_inv[6,2], '/', lik_inv[6,2])
F2n <- paste("Fb: No hard cap", 'Mean:', lik_no_inv[7,1], t_no_inv[7,5], '/',  lik_inv[7,1], t_inv[7,5], "Idk:", lik_no_inv[7,2], '/', lik_inv[7,2])
F3n <- paste("Fc:  The team has diverse knowledge", 'Mean:', lik_no_inv[8,1], t_no_inv[8,5], '/',  lik_inv[8,1], t_inv[8,5], "Idk:", lik_no_inv[8,2], '/', lik_inv[8,2])
F4n <- paste("Fd: The venture has an advisory board", 'Mean:', lik_no_inv[9,1], t_no_inv[9,5], '/',  lik_inv[9,1], t_inv[9,5], "Idk:", lik_no_inv[9,2], '/', lik_inv[9,2])
F5n <- paste("Fe: The venture is backed by a venture capitalist", 'Mean:', lik_no_inv[10,1], t_no_inv[10,5],  '/',  lik_inv[10,1], t_inv[10,5], "Idk:", lik_no_inv[10,2], '/', lik_inv[10,2])
F6n <- paste("Ff: The venture is backed by a corporate venture capitalist", 'Mean:', lik_no_inv[11,1], t_no_inv[11,5], '/',  lik_inv[11,1], t_inv[11,5], "Idk:", lik_no_inv[11,2], '/', lik_inv[11,2])
F7n <- paste("Fg: The venture is backed by a venture capitalist with experience in the blockchain sector", 'Mean:', lik_no_inv[12,1], t_no_inv[12,5], '/',  lik_inv[12,1], t_inv[12,5], "Idk:", lik_no_inv[12,2], '/', lik_inv[12,2])
F8n <- paste("Fh: The venture is backed by a venture capitalist whose tokens are locked up", 'Mean:', lik_no_inv[13,1], t_no_inv[13,5], '/',  lik_inv[13,1], t_inv[13,5], "Idk:", lik_no_inv[13,2], '/', lik_inv[13,2])
F9n <- paste("Fi: The venture has a high expert team rating", 'Mean:', lik_no_inv[14,1], t_no_inv[14,5],  '/',  lik_inv[14,1], t_inv[14,5], "Idk:", lik_no_inv[14,2], '/', lik_inv[14,2])
F10n <- paste("Fj: The venture has a high expert vision rating", 'Mean:', lik_no_inv[15,1], t_no_inv[15,5], '/',  lik_inv[15,1], t_inv[15,5], "Idk:", lik_no_inv[15,2], '/', lik_inv[15,2])
F11n <- paste("Fk: The venture has a high expert product rating", 'Mean:', lik_no_inv[16,1], t_no_inv[16,5],  '/',  lik_inv[16,1], t_inv[16,5], "Idk:", lik_no_inv[16,2], '/', lik_inv[16,2])
F12n <- paste("Fl:  The offering period is short", 'Mean:', lik_no_inv[17,1], t_no_inv[17,5], '/',  lik_inv[17,1], t_inv[17,5], "Idk:", lik_no_inv[17,2], '/', lik_inv[17,2])
F13n <- paste("Fm:  The website provides plenty of crypto related information", 'Mean:', lik_no_inv[18,1], t_no_inv[18,5], '/',  lik_inv[18,1], t_inv[18,5], "Idk:", lik_no_inv[18,2], '/', lik_inv[18,2])
F14n <- paste("Fn: The venture is highly active on Twitter", 'Mean:', lik_no_inv[19,1], t_no_inv[19,5], '/',  lik_inv[19,1], t_inv[19,5], "Idk:", lik_no_inv[19,2], '/', lik_inv[19,2])
F15n <- paste("Fo: A pre-sale was conducted before the token offering", 'Mean:', lik_no_inv[20,1], t_no_inv[20,5], '/',  lik_inv[20,1], t_inv[20,5], "Idk:", lik_no_inv[20,2], '/', lik_inv[20,2])
F16n <- paste("Fp: The venture offers a small share of tokens to investors", 'Mean:', lik_no_inv[21,1], t_no_inv[21,5], '/',  lik_inv[21,1], t_inv[21,5], "Idk:", lik_no_inv[21,2], '/', lik_inv[21,2])
F17n <- paste("Fq:  Incentive pool for employees", 'Mean:', lik_no_inv[22,1], t_no_inv[22,5], '/',  lik_inv[22,1], t_inv[22,5], "Idk:", lik_no_inv[22,2], '/', lik_inv[22,2])
F18n <- paste("Fr:  Lock up for team and founders", 'Mean:', lik_no_inv[23,1], t_no_inv[23,5], '/',  lik_inv[23,1], t_inv[23,5], "Idk:", lik_no_inv[23,2], '/', lik_inv[23,2])
F19n <- paste("Fs: Disclosed budget use plan", 'Mean:', lik_no_inv[24,1], t_no_inv[24,5], '/',  lik_inv[24,1], t_inv[24,5], "Idk:", lik_no_inv[24,2], '/', lik_inv[24,2])
F20n <- paste("Ft:  Milestone plan for fund release", 'Mean:', lik_no_inv[25,1], t_no_inv[25,5], '/',  lik_inv[25,1], t_inv[25,5], "Idk:", lik_no_inv[25,2], '/', lik_inv[25,2])
F21n <- paste("Fu: Funds are stored in a wallet which enables access only if multiple people work together", 'Mean:', lik_no_inv[26,1], t_no_inv[26,5], '/',  lik_inv[26,1], t_inv[26,5], "Idk:", lik_no_inv[26,2], '/', lik_inv[26,2])
F22n <- paste("Fv:  The funds are managed by an independent custodian", 'Mean:', lik_no_inv[27,1], t_no_inv[27,5],  '/',  lik_inv[27,1], t_inv[27,5], "Idk:", lik_no_inv[27,2], '/', lik_inv[27,2])
F23n <- paste("Fw:  The tokens are offered in stages", 'Mean:', lik_no_inv[28,1], t_no_inv[28,5], '/',  lik_inv[28,1], t_inv[28,5], "Idk:", lik_no_inv[28,2], '/', lik_inv[28,2])

#country:
F24n <- paste("Fca: United States of America", 'Mean:', lik_no_inv[29,1], t_no_inv[29,5], '/',  lik_inv[29,1], t_inv[29,5], "Idk:", lik_no_inv[29,2], '/', lik_inv[29,2])
F25n <- paste("Fcb: Singapore", 'Mean:', lik_no_inv[30,1], t_no_inv[30,5], '/',  lik_inv[30,1], t_inv[30,5], "Idk:", lik_no_inv[30,2], '/', lik_inv[30,2])
F26n <- paste("Fcc: United Kingdom", 'Mean:', lik_no_inv[31,1], t_no_inv[31,5], '/',  lik_inv[31,1], t_inv[31,5], "Idk:", lik_no_inv[31,2], '/', lik_inv[31,2])
F27n <- paste("Fcd: Russia", 'Mean:', lik_no_inv[32,1], t_no_inv[32,5],  '/',  lik_inv[32,1], t_inv[32,5], "Idk:", lik_no_inv[32,2], '/', lik_inv[32,2])
F28n <- paste("Fce: Switzerland", 'Mean:', lik_no_inv[33,1], t_no_inv[33,5],  '/',  lik_inv[33,1], t_inv[33,5], "Idk:", lik_no_inv[33,2], '/', lik_inv[33,2])
#Experience
F29n <- paste("Fea: Managerial experience as a top manager", 'Mean:', lik_no_inv[34,1], t_no_inv[34,5], '/',  lik_inv[34,1], t_inv[34,5], "Idk:", lik_no_inv[34,2], '/', lik_inv[34,2])
F30n <- paste("Feb: Entrepreneurial experience", 'Mean:', lik_no_inv[35,1], t_no_inv[35,5], '/',  lik_inv[35,1], t_inv[35,5], "Idk:", lik_no_inv[35,2], '/', lik_inv[35,2])
F31n <- paste("Fec: Technical experience", 'Mean:', lik_no_inv[36,1], t_no_inv[36,5], '/',  lik_inv[36,1], t_inv[36,5], "Idk:", lik_no_inv[36,2], '/', lik_inv[36,2])
F32n <- paste("Fed: Holds a Ph.D", 'Mean:', lik_no_inv[37,1], t_no_inv[37,5], '/',  lik_inv[37,1], t_inv[37,5], "Idk:", lik_no_inv[37,2], '/', lik_inv[37,2])

colnames(ds_f_sig) <- c('Investor group', F1n, F2n, F3n, F4n, F5n, F6n, F7n, F8n, F9n, F10n, F11n, F12n, F13n, F14n, F15n, F16n, F17n, F18n, F19n, F20n, F21n, F22n, F23n, F24n, F25n, F26n, F27n, F28n, F29n, F30n, F31n, F32n)

likert_f_sig <- ds_f_sig[,1:33] %>%
  dplyr::mutate_if(is.character, factor) %>%
  dplyr::mutate_if(is.numeric, factor, levels = 1:5, labels = lbs) %>%
  #drop_na() %>% #drops IDK?
  as.data.frame()

likert_plot_f_sig <- plot(likert(likert_f_sig[,2:24], grouping = likert_f_sig[,1])) #grouped by investor group

#cowplot::save_plot(here("plot", "likert_plot_f_sig.png"), # where to save the plot
 #                  likert_plot_f_sig,        # object to plot
  #                 base_asp = 1.5,  # ratio of space fro questions vs space for plot
   #                base_height = 6) # size! higher for smaller font size

likert_plot_country <- plot(likert(likert_f_sig[,25:29], grouping = likert_f_sig[,1])) #grouped by investor group

cowplot::save_plot(here("plot", "likert_plot_country.png"), # where to save the plot
                   likert_plot_country,        # object to plot
                   base_asp = 1.5,  # ratio of space fro questions vs space for plot
                   base_height = 6) # size! higher for smaller font size

likert_plot_founder_exp <- plot(likert(likert_f_sig[,30:33], grouping = likert_f_sig[,1])) #grouped by investor group

cowplot::save_plot(here("plot", "likert_plot_founder_exp.png"), # where to save the plot
                   likert_plot_founder_exp,        # object to plot
                   base_asp = 1.5,  # ratio of space fro questions vs space for plot
                   base_height = 6) # size! higher for smaller font size


#ideological signals
I1n <- paste("Ia: The token is based on the Ethereum blockchain", 'Mean:', lik_no_inv[38,1], t_no_inv[38,5], '/',  lik_inv[38,1], t_inv[38,5], "Idk:", lik_no_inv[38,2], '/', lik_inv[38,2])
I2n <- paste("Ib: The token offers voting rights", 'Mean:', lik_no_inv[39,1], t_no_inv[39,5], '/',  lik_inv[39,1], t_inv[39,5], "Idk:", lik_no_inv[39,2], '/', lik_inv[39,2])
I3n <- paste("Ic: A smart contract custodian which transacts money to the venture with a pre-defined function", 'Mean:', lik_no_inv[40,1], t_no_inv[40,5], '/',  lik_inv[40,1], t_inv[40,5], "Idk:", lik_no_inv[40,2], '/', lik_inv[40,2])
I4n <- paste("Id: A smart contract custodian which transacts money to the venture with a pre-defined function,
at a certain event or milestone after the offering", 'Mean:', lik_no_inv[41,1], t_no_inv[41,5], '/',  lik_inv[41,1], t_inv[41,5], "Idk:", lik_no_inv[41,2], '/', lik_inv[41,2])
I5n <- paste("Ie: A smart contract custodian which transacts money to the venture with a pre-defined function,
at a certain event or milestone with a voting right according to the events after the offering", 'Mean:', lik_no_inv[42,1], t_no_inv[42,5], '/',  lik_inv[42,1], t_inv[42,5], "Idk:", lik_no_inv[42,2], '/', lik_inv[42,2])
I6n <- paste("If: Token holders can vote on a liquidation and get the locked money back", 'Mean:', lik_no_inv[43,1], t_no_inv[43,5], '/',  lik_inv[43,1], t_inv[43,5], "Idk:", lik_no_inv[43,2], '/', lik_inv[43,2])
I7n <- paste("Ig: Providing liquidity through a token pair on Uniswap", 'Mean:', lik_no_inv[44,1], t_no_inv[44,5], '/',  lik_inv[44,1], t_inv[44,5], "Idk:", lik_no_inv[44,2], '/', lik_inv[44,2])

colnames(ds_i_sig) <- c('Investor group', I1n, I2n, I3n, I4n, I5n, I6n, I7n)

likert_i_sig <- ds_i_sig %>%
  dplyr::mutate_if(is.character, factor) %>%
  dplyr::mutate_if(is.numeric, factor, levels = 1:5, labels = lbs) %>%
  #drop_na() %>% #drops IDK?
  as.data.frame()

likert_plot_i_sig <- plot(likert(likert_i_sig[,2:8], grouping = likert_f_sig[,1])) #grouped by investor group

cowplot::save_plot(here("plot", "likert_plot_i_sig.png"), # where to save the plot
                   likert_plot_i_sig,        # object to plot
                   base_asp = 1.5,  # ratio of space fro questions vs space for plot
                   base_height = 6) # size! higher for smaller font size


```

t-tests for H7, H17, H18, H23
```{r}
H7 <- data.frame(ds_inv$TS01_01, ds_inv$TS01_05)
H7[H7 == -1] <- NA #replaces every -1 with a NA
t.test(H7[,2], H7[,1], alternative = "greater")

H17a <- data.frame(ds_inv$FS01_08, ds_inv$FS01_06)
H17a[H17a == -1] <- NA #replaces every -1 with a NA
t.test(H17a[,1], H17a[,2], alternative = "greater")

H17b <- data.frame(ds_no_inv$FS01_08, ds_no_inv$FS01_06)
H17b[H17b == -1] <- NA #replaces every -1 with a NA
t.test(H17b[,1], H17b[,2], alternative = "greater")

H18a <- data.frame(ds_inv$FS01_09, ds_inv$FS01_06)
H18a[H18a == -1] <- NA #replaces every -1 with a NA
t.test(H18a[,1], H18a[,2], alternative = "greater")

H18b <- data.frame(ds_no_inv$FS01_09, ds_no_inv$FS01_06)
H18b[H18b == -1] <- NA #replaces every -1 with a NA
t.test(H18b[,1], H18b[,2], alternative = "greater")

H23a <- data.frame(ds_inv$FS02_15, ds_inv$FS02_11)
H23a[H23a == -1] <- NA #replaces every -1 with a NA
t.test(H23a[,1], H23a[,2], alternative = "greater")

H23b <- data.frame(ds_no_inv$FS02_15, ds_no_inv$FS02_11)
H23b[H23b == -1] <- NA #replaces every -1 with a NA
t.test(H23b[,1], H23b[,2], alternative = "greater")

```

Factor analysis
n SPSS a convenient option is offered to check whether the sample is big enough: the 
Kaiser-Meyer-Olkin measure of sampling adequacy (KMO-test). The sample is adequate if 
the value of KMO is greater than 0.5. Furthermore, SPSS can calculate an anti-image matrix 
of covariances and correlations. All elements on the diagonal of this matrix should be greater 
than 0.5 if the sample is adequate (Field 2000: 446)
```{r}
KMOS(ds_sig)
```

Free text critic
```{r}
ds$E003_01[!is.na(ds$E003_01)]
```

Session info to reproduce
```{r}
sessionInfo()
```

